Verifying Demonstrations

### 2020-03-13 paper/DB-Schnorr-PKI.tex

All \acl{DB} protocols requires hardware 
implementations~\cite{DBonSmartphones}.
We will use a \emph{trusted} hardware implementation to overcome the limitation 
of \textcite{UWBPR}, \ie that the prover and verifier must be mutually trusted.
We will need \iac{PKI} for the verifier to verify the trusted hardware.
We will leverage this \ac{PKI} to overcome the shared-key requirement to allow 
any two devices in this \ac{PKI} to perform \acl{DB}.
With \iac{PKI} based on discrete logarithms we will be able to perform \iac{DB} 
\ac{ZKPK} which \emph{simultaneously} proves
\begin{enumerate*}
\item that the protocol is run by trusted hardware,
\item that that trusted hardware is within proximity,
\item that some \ac{ZKPK} statement about some discrete logarithms holds, and
\item that that knowledge is within proximity.
\end{enumerate*}

@@

In summary, the difference is as follows.
\(\DBS\) has a static shared key~\(k\) and performs \(
  \PK[\alpha][A = g^\alpha]
\) with a distance bound.
\(\DBSHW\) first runs \iac{DHKE} to establish the shared key~\(k =
\gDH^{\xDH \yDH}\) from \(\XDH = \gDH^{\xDH}, \YDH = \gDH^{\yDH}\), then 
performs \[
  \PK[\alpha, \xDH, \sk_P, \sigma][
    A = g^\alpha \land
    \XDH = \gDH^{\xDH} \land
    \XDHCL = \XDH^{\sk} \land
    \Blind[\sigma] = \Sign[_{\sk}][\sk_P]
  ],
\] also with a distance bound; where \(\sk_P\) is the prover's private key, 
\(\sigma\) is a signature issued with signing key~\(\sk\) and \(\Blind\) 
reblinds a signature.
Proving knowledge of \(\XDH = \gDH^{\xDH}\) and \(\XDHCL = \XDH^{\sk}\) 
prevents any \ac{MITM} attack against the \ac{DHKE}.
Proving knowledge of a signature~\(\sigma\) by \iac{CA} on the private 
key~\(\sk_P\) ensures that the prover is a device in the \ac{PKI} of the 
\ac{CA}.

@@

To answer the first question,
by \textcite{Camenisch-phdthesis}, the above protocol is \iac{ZKPK}.
In the case of \iac{MITM}, the prover will run the protocol using \(\XDH\) and 
\(\sk\), while the verifier will use \(\XDH'\), possibly modified by the 
adversary.
The adversary's goal is to pass as knowing \(\sk\) and its signature (to 
impersonate real hardware).
The \(\sk\) must be the same \(\sk\) throughout the 
subproofs~\cite{Camenisch-phdthesis}.
In one subprotocol, the prover will prove knowledge of \(\XDH^{\sk}\).
If \(\XDH' \neq \XDH\) used by the verifier is wrong, then by soundness the 
proof will fail.

>>>>

All \acl{DB} protocols requires hardware 
implementations~\cite{DBonSmartphones}.
We will use a \emph{trusted} hardware implementation to overcome the limitation 
of \textcite{UWBPR}, \ie that the prover and verifier must share a key.
We will provide \iac{PKI} for the verifier to verify the trusted hardware.
We will leverage this \ac{PKI} to overcome the shared-key requirement to allow 
any two devices in this \ac{PKI} to perform \acl{DB}.
With \iac{PKI} based on discrete logarithms we will be able to perform \iac{DB} 
\ac{ZKPK} which \emph{simultaneously} proves
\begin{enumerate*}
\item that the protocol is run by trusted hardware,
\item that that trusted hardware is within proximity,
\item that some \ac{ZKPK} statement about some discrete logarithms holds, and
\item that that knowledge is within proximity.
\end{enumerate*}

@@

In summary, the difference is as follows.
\(\DBS\) performs \(
  \PK[\alpha][A = g^\alpha]
\) with a distance bound on the user's behalf.
\(\DBSHW\) first runs \iac{DHKE} to establish a shared key~\(k =
\gDH^{\xDH \yDH}\) from \(\XDH = \gDH^{\xDH}, \YDH = \gDH^{\yDH}\), then 
performs \[
  \PK[\alpha, \xDH, \sk_P, \sigma][
    A = g^\alpha \land
    \XDH = \gDH^{\xDH} \land
    \XDHCL = \XDH^{\sk} \land
    \Blind[\sigma] = \Sign[_{\sk}][\sk_P]
  ],
\] also with a distance bound and \(A = g^\alpha\) on behalf of the user; where 
\(\sk_P\) is the prover's private key, \(\sigma\) is a signature issued with 
signing key~\(\sk\) and \(\Blind\) reblinds a signature.
Proving knowledge of \(\XDH = \gDH^{\xDH}\) and \(\XDHCL = \XDH^{\sk}\) 
prevents any \ac{MITM} attack against the \ac{DHKE}.
Proving knowledge of a signature~\(\sigma\) by \iac{CA} on the private 
key~\(\sk_P\) ensures that the prover is a device in the \ac{PKI} of the 
\ac{CA}.

@@

To answer the first question,
by \textcite{Camenisch-phdthesis}, the above protocol is \iac{ZKPK}.
In the case of \iac{MITM}, the prover will run the protocol using \(\XDH\) and 
\(\sk\), while the verifier will use \(\XDH'\), possibly modified by the 
adversary.
The adversary's goal is to pass as knowing \(\sk\) and its signature (to 
impersonate real hardware).
The \(\sk\) must be the same \(\sk\) throughout the 
subprotocols~\cite{Camenisch-phdthesis}.
In one subprotocol, the prover will prove knowledge of \(\XDH^{\sk}\).
If \(\XDH' \neq \XDH\) used by the verifier is wrong, then by soundness the 
proof will fail.
